Enhancing Accelerometer-based Activity Recognition with Capacitive Proximity Sensing

### 2012-06-20 Paper/Paper.tex
results
image added and references fixed  - wristband with electrodes and sensors  - removed urls from references

\begin{figure}[htbp]
	\centering
		\includegraphics[width=1.00\textwidth]{Images/schematic.pdf}
	\caption{The sensing circuit is based on a timer with an operational amplifier that acts as a voltage follower. The wire that is labeled with "`antenna"' leads to the sensing electrode, whereas the wire labeled with "`guard"' leads to the shield electrode.}
	\label{fig:schematic}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
 		\includegraphics[trim=1cm 1cm 1cm 1cm,clip,width=\textwidth]{Images/pseudocode.pdf}
	\caption{Measurement procedure}
	\label{fig:pseudocode}
\end{figure}

>>>>

\begin{figure}
	\centering
		\includegraphics[width=1.00\textwidth]{Images/schematic.pdf}
	\caption{The sensing circuit is based on a timer with an operational amplifier that acts as a voltage follower. The wire that is labeled with ``antenna'' leads to the sensing electrode, whereas the wire labeled with ``guard'' leads to the shield electrode.}
	\label{fig:schematic}
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[width=1.00\textwidth]{Images/capacitive_sensor_wristband_2.jpg}
	\caption{The hardware prototype at a glance: HedgeHog activity logger at the lower right, the capacitive sensor unit at the lower left, and the wristband with the sensing and the shield electrodes on-top each other covered with adhesive tape for isolation purposes.}
	\label{fig:cap_sensor}
\end{figure}

Figure \ref{fig:cap_sensor} shows the the wrist-worn prototype used in the evaluation experiments, with the HedgeHog as the main data logger, the capacitive sensor circuit and the wristband holding the sensing and shielding electrodes.

\begin{figure}
	\centering
 		\includegraphics[trim=1cm 1cm 1cm 1cm,clip,width=\textwidth]{Images/pseudocode.pdf}
	\caption{Measurement procedure carried out by the HedgeHog sensor: using the microcontroller's Timer0 module in counting mode, the oscillating signal generated by the capacitive sensor circuit can be measured by counting the frequency pulses over a predefined gate time (approximately 9.5ms).}
	\label{fig:pseudocode}
\end{figure}
